--- 
title       : Interactive Noise/Error Manipulation 
subtitle    : An "Interactive Shiny Project" Presentation Pitch
author      : dd1947in
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---bg:url(assets/fig/shiny_proj.png)

---   

## A Very Brief Description  
  One can study and get better in any subject  with the use of interactive applications . Interactive applications are very important tools to demonstrate  products and ideas to a wider audience.   This presentation is submitted to pitch an "Interactive Shiny Project".  
  
   The following slides show a a list of plots  that are generated in "Interactive Shiny Project"  that accompany these project pitch  slides .  The following methodology  is followed in the design of the "Interactive Shiny Project".  

1. Points (x, y)   on a reference line  y = s1 * x + c1  are generated for a given slope and intercept. 
2. Points (x, y)  on a noisy line yo = y + random_normal_error(mean_err, sd_err)  are generated  for a given mean and sd .  
3. A linear regression model  is fit through reference line and noisy line . 
4. User is given Plot options  of Points  and Line/Smooth. 
5. User can manipultate slope, intercept, mean of error, sd of error and create new plots .
6. User can study the effects of various parameters on the  reference and noisy lines . 

--- .class #id 

### Plot 1 : Beta = 1; Y-int = 0; Mean = 0; SD = 0 ; Type = point

```{r echo=FALSE}

library(ggplot2)

      x <- seq(from=0, to=500, by=10)
      beta <- 1
      yint <- 0
      mean1 <- 0
      sd1 <- 0 
      plot_type <- "point"
      y <-  x * beta + yint   

      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      


      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)


      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
       
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green" ),  size=2  ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }
      
      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
    
```


---  

### Plot 2 : Beta = 1; Y-int = 0; Mean = 0; SD = 50 ; Type = point

```{r echo=FALSE}
      beta <- 1 
      yint <- 0
      mean1 <- 0
      sd1 <- 50 
      plot_type <- "point"
      y <-  x * beta + yint   

      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      

      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)
       
      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green" ),  size=2  ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }
      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
    
```



---  

### Plot 3 : Beta = 1; Y-int = 0; Mean = -50; SD = 50 ; Type = point

```{r echo=FALSE}
      beta <- 1 
      yint <- 0
      mean1 <- -50
      sd1 <- 50 
      plot_type <- "point"
      ya <-  x * beta + yint   

      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      


      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)
       
      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green" ),  size=2  ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }
      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
    
```

---  

### Plot 4 : Beta = 1; Y-int = 0; Mean = 50; SD = 50 ; Type = point

```{r echo=FALSE}
      beta <- 1 
      yint <- 0
      mean1 <- 50
      sd1 <- 50 
      plot_type <- "point"
      ya <-  x * beta + yint  

      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      


      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)
       
      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green" ),  size=2  ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }
      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
    
```

---  

### Plot 5 : Beta = 1; Y-int = 0; Mean = -50; SD = 50 ; Type = line/smooth  
  

```{r echo=FALSE}
      beta <- 1 
      yint <- 0
      mean1 <- -50
      sd1 <- 50 
      plot_type <- "line"
      y <-  x * beta + yint    


      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      


      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)
       
      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green" ),  size=2  ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }

      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
    
```

---   
    

### Plot 6 : Beta = 1; Y-int = 0; Mean = 50; SD = 50 ; Type = line/smooth  
  
  
```{r echo=FALSE}
      beta <- 1 
      yint <- 0
      mean1 <- 50
      sd1 <- 50 
      plot_type <- "line"
      y <-  x * beta + yint  

      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      



      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)
       
      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green"  ),  size=2 ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }
      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
    
```

---  

### Plot 7 : Beta = -1; Y-int = 0; Mean = 0; SD = 0 ; Type = point  
  

```{r echo=FALSE}
      beta <- -1 
      yint <- 300
      mean1 <- -50
      sd1 <- 50 
      plot_type <- "point"
      y <-  x * beta + yint    

      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      


      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)
       
      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green" ),  size=2  ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }
      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
    
```

---  

### Plot 8 : Beta = -1; Y-int = 300; Mean = 50; SD = 50 ; Type = point  
     

```{r echo=FALSE}
      beta <- -1 
      yint <- 300
      mean1 <- 50
      sd1 <- 50 
      plot_type <- "point"
      y <-  x * beta + yint  

      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      


      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)
       
      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green" ),  size=2  ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }
      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
    
```

---   
   
   
### Plot 9 : Beta = 1; Y-int = 0; Mean = -50; SD = 0 ; Type = point  
   
   
```{r echo=FALSE}
      beta <- 1 
      yint <- 0
      mean1 <- -50
      sd1 <- 0 
      plot_type <- "point"
      y <-  x * beta + yint  

      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      


      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)
       
      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green" ),  size=2  ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }
      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
```   

---     
   
### Plot 10 : Beta = 1; Y-int = 0; Mean = 50; SD = 0 ; Type = point  
  

```{r echo=FALSE}
      beta <- 1 
      yint <- 0
      mean1 <- 50
      sd1 <- 0 
      plot_type <- "point"
      y <-  x * beta + yint  

      y1 = yint
      y2 = yint + 500 * beta
      if(y1 > y2) {
        ymax = y1
      } else {
        ymax = y2
      }
      # this is for positioning text labels on plot
      ymax = abs(500 * beta) * 2.0  + abs(sd1 + 200) * 1.25
      yfactor =  ymax / 750 
      


      yo <- y + rnorm(length(x), mean=mean1, sd=sd1)
      dfa_xy <- data.frame(x=x, y=y, yo=yo)
      
      lmfit_o <- lm(yo ~ x, data=dfa_xy)
      lmfit_a <- lm(y ~ x, data=dfa_xy)
       
      xfit <- c(0, 500)
      yfit <- c (lmfit_o$coeff[1][1], 500 * lmfit_o$coeff[2][1] +lmfit_o$coeff[1][1])
      dfo_xy <- data.frame(x=xfit, y=yfit)
      
      
      g <- ggplot(dfa_xy) 
      if(plot_type == "point") {
            g <- g + geom_point(aes(x=x, y=y,  colour="green" ) ) + geom_point(aes(x=x, y=yo, colour="red")) 
      } else {
             g <- g + geom_smooth(aes(x=x, y=y,  colour="green" ),  size=2  ) + geom_smooth(aes(x=x, y=yo, colour="red"),  size=2 ) 

      }
      g <- g + annotate("text", x=80, y=ymax - 10 * yfactor, label = paste("Reference Line Slope = ", round(lmfit_a$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 40 * yfactor, label = paste("Reference Line Y-Int = ", round(lmfit_a$coeff[1][1], 4)))
      
       
      g <- g + annotate("text", x=80, y=ymax - 90 * yfactor, label = paste("Noisy line Slope = ", round(lmfit_o$coeff[2][1], 4)))
      g <- g + annotate("text", x=80, y=ymax - 120 * yfactor, label = paste("Noisy Line Y-Int = ", round(lmfit_o$coeff[1][1], 4)))      
      g <- g + geom_line(data=dfo_xy, aes(x=x, y=y,  colour="1" ), linetype=1)
      g <- g + geom_line( aes(x=x, y=y,  colour="10" ), linetype=1)
      g
    
```